---
title: "Prescription_aggregation"
author: "Peter B"
date: "5 May 2018"
output: html_document
---

```{r setup, include=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "C:/Users/Peter/Downloads/Data/")
```

## libraries
This is the list of libraries used in the exploration

```{r, echo=FALSE}
rm(list = ls())
library(dendextend)
library(feather)
library(forcats)
library(lubridate)
library(scales)
library(GGally)
library(cowplot)
library(Rtsne)
library(clValid)
library(scales)
library(corrplot)
library(sqldf)
library(ggplot2)
library(magrittr)
library(tidyverse)
library(reshape2)
library(lubridate)
library(e1071)
library(Deducer)
library(factoextra)
library(leaflet)
library(rgdal)
library(sp)
library(maptools)
library(raster)
library(RColorBrewer)
library(readxl)
library(data.table)


```

## Prescription

Lets load in the data and take a look at the data.
The data has a number of fields:
 1. Urn
 2. Lsoa
 3. Postcode (we can group up at postcode level to oa)
 4. postcode population
 5. bnf_chapter
 6. number_of_prescriptions
 7. nic
 8. actual_cost
 9. month

```{r}
getwd()
```



## Lets read in all the cardio data

```{r, echo=FALSE}
getwd()

file_names <- dir("./CARDIOVASCULAR") #where you have your files

print(file_names)

Cardio <- do.call(rbind,lapply(paste("./CARDIOVASCULAR/",file_names,sep=""),read_tsv))
colnames<-NULL

colnames(Cardio)


Cardio %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  ) %>% ungroup() -> Cardio_sum_lsoa



Cardio_sum_lsoa$Drug<-"Cardiovascular"

Cardio<-NULL

```


## Lets read in all the CNS data

```{r, echo=FALSE}

##CentralNervousSystem

file_names <- dir("./CentralNervousSystem") #where you have your files

print(file_names)

CentralNervousSystem <- do.call(rbind,lapply(paste("./CentralNervousSystem/",file_names,sep=""),read_tsv))

colnames(CentralNervousSystem)


CentralNervousSystem %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> CentralNervousSystem_sum_lsoa



CentralNervousSystem_sum_lsoa$Drug<-"Central Nervous System"

CentralNervousSystem<-NULL

```


## Lets read in all the Ear, Nose and Throat data


```{r, echo=FALSE}

##EarNoseandOropharynx

file_names <- dir("./EarNoseandOropharynx") #where you have your files

print(file_names)

EarNoseandOropharynx <- do.call(rbind,lapply(paste("./EarNoseandOropharynx/",file_names,sep=""),read_tsv))

colnames(EarNoseandOropharynx)


EarNoseandOropharynx %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> EarNoseandOropharynx_sum_lsoa



EarNoseandOropharynx_sum_lsoa$Drug<-"Ear, Nose and Oropharynx"

EarNoseandOropharynx<-NULL
```

## Lets read in all the Ear, Nose and Throat data

```{r, echo=FALSE}
#EndocrineSystem

file_names <- dir("./EndocrineSystem") #where you have your files

print(file_names)

EndocrineSystem <- do.call(rbind,lapply(paste("./EndocrineSystem/",file_names,sep=""),read_tsv))

colnames(EndocrineSystem)


EndocrineSystem %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup()  -> EndocrineSystem_sum_lsoa



EndocrineSystem_sum_lsoa$Drug<-"Endocrine System"

EndocrineSystem<-NULL

```

## Eye

```{r, echo=FALSE}

file_names <- dir("./Eye") #where you have your files

print(file_names)

Eye <- do.call(rbind,lapply(paste("./Eye/",file_names,sep=""),read_tsv))

colnames(EndocrineSystem)


Eye %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> Eye_sum_lsoa



Eye_sum_lsoa$Drug<-"Eye"

Eye<-NULL


```

## Ear, Nose and Oropharynx

```{r, echo=FALSE}
##EarNoseandOropharynx

file_names <- dir("./EarNoseandOropharynx") #where you have your files

print(file_names)

EarNoseandOropharynx <- do.call(rbind,lapply(paste("./EarNoseandOropharynx/",file_names,sep=""),read_tsv))

colnames(EarNoseandOropharynx)


EarNoseandOropharynx %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup()  -> EarNoseandOropharynx_sum_lsoa



EarNoseandOropharynx_sum_lsoa$Drug<-"Ear, Nose and Oropharynx"

EarNoseandOropharynx<-NULL
```

## Lets read in all the Gastro Intestinal System data

```{r, echo=FALSE}
#GastroIntestinalSystem

file_names <- dir("./GastroIntestinalSystem") #where you have your files

print(file_names)

GastroIntestinalSystem <- do.call(rbind,lapply(paste("./GastroIntestinalSystem/",file_names,sep=""),read_tsv))

colnames(GastroIntestinalSystem)


GastroIntestinalSystem %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> GastroIntestinalSystem_sum_lsoa



GastroIntestinalSystem_sum_lsoa$Drug<-"Gastro Intestinal System"

GastroIntestinalSystem<-NULL

```
 


## Lets read in all the Gastro Intestinal System data

```{r, echo=FALSE}
#ImmunologicalProductsVaccines

file_names <- dir("./ImmunologicalProductsVaccines") #where you have your files

print(file_names)

ImmunologicalProductsVaccines <- do.call(rbind,lapply(paste("./ImmunologicalProductsVaccines/",file_names,sep=""),read_tsv))

colnames(ImmunologicalProductsVaccines)


ImmunologicalProductsVaccines %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> ImmunologicalProductsVaccines_sum_lsoa



ImmunologicalProductsVaccines_sum_lsoa$Drug<-"Immunological Products Vaccines"

ImmunologicalProductsVaccines<-NULL

```
 
## Infections

```{r,echo=FALSE}
#Infections

file_names <- dir("./Infections") #where you have your files

print(file_names)

Infections <- do.call(rbind,lapply(paste("./Infections/",file_names,sep=""),read_tsv))

colnames(Infections)


Infections %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> Infections_sum_lsoa



Infections_sum_lsoa$Drug<-"Infections"

Infections<-NULL


```

## IncontinenceAppliances

```{r, echo=FALSE}
#IncontinenceAppliances

file_names <- dir("./IncontinenceAppliances") #where you have your files

print(file_names)

IncontinenceAppliances <- do.call(rbind,lapply(paste("./IncontinenceAppliances/",file_names,sep=""),read_tsv))

colnames(IncontinenceAppliances)


IncontinenceAppliances %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> IncontinenceAppliances_sum_lsoa



IncontinenceAppliances_sum_lsoa$Drug<-"Incontinence Appliances"

IncontinenceAppliances<-NULL


```

## ImmunologicalProductsVaccines

```{r, echo=FALSE}
#ImmunologicalProductsVaccines

file_names <- dir("./ImmunologicalProductsVaccines") #where you have your files

print(file_names)

ImmunologicalProductsVaccines <- do.call(rbind,lapply(paste("./ImmunologicalProductsVaccines/",file_names,sep=""),read_tsv))

colnames(ImmunologicalProductsVaccines)


ImmunologicalProductsVaccines %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  )  %>% ungroup() -> ImmunologicalProductsVaccines_sum_lsoa



ImmunologicalProductsVaccines_sum_lsoa$Drug<-"Immunological Products Vaccines"

ImmunologicalProductsVaccines<-NULL

```

## Malignant Disease Immunosuppression

```{r, echo=FALSE}
#ImmunologicalProductsVaccines

file_names <- dir("./MalignantDiseaseImmunosuppression") #where you have your files

print(file_names)

MalignantDiseaseImmunosuppression <- do.call(rbind,lapply(paste("./MalignantDiseaseImmunosuppression/",file_names,sep=""),read_tsv))

colnames(MalignantDiseaseImmunosuppression)


MalignantDiseaseImmunosuppression %>% dplyr::select(lsoa,month,postcode_population,number_of_prescriptions,nic,actual_cost) %>% group_by(lsoa,month) %>%
  summarize_all(sum, na.rm=TRUE)  %>% mutate(
    number_of_prescriptions_std=number_of_prescriptions/postcode_population,
    nic_std=nic/postcode_population,
    actual_cost_std=actual_cost/postcode_population
  ) %>% ungroup() -> MalignantDiseaseImmunosuppression_sum_lsoa



MalignantDiseaseImmunosuppression_sum_lsoa$Drug<-"MalignantDiseaseImmunosuppression"

MalignantDiseaseImmunosuppression<-NULL

```


## Join everything together 

```{r,echo=FALSE}

MalignantDiseaseImmunosuppression_sum_lsoa<-MalignantDiseaseImmunosuppression_sum_lsoa %>% as.data.frame()

ImmunologicalProductsVaccines_sum_lsoa<-ImmunologicalProductsVaccines_sum_lsoa %>% as.data.frame()

IncontinenceAppliances_sum_lsoa<-IncontinenceAppliances_sum_lsoa %>% as.data.frame()

Infections_sum_lsoa<-Infections_sum_lsoa %>% as.data.frame()

GastroIntestinalSystem_sum_lsoa<-GastroIntestinalSystem_sum_lsoa %>% as.data.frame()

EarNoseandOropharynx_sum_lsoa<-EarNoseandOropharynx_sum_lsoa %>% as.data.frame()

EndocrineSystem_sum_lsoa<-EndocrineSystem_sum_lsoa %>% as.data.frame()

CentralNervousSystem_sum_lsoa<-CentralNervousSystem_sum_lsoa %>% as.data.frame()

Cardio_sum_lsoa<-Cardio_sum_lsoa %>% as.data.frame()

my.df.list= list(MalignantDiseaseImmunosuppression_sum_lsoa,
ImmunologicalProductsVaccines_sum_lsoa,
IncontinenceAppliances_sum_lsoa,
Infections_sum_lsoa,
GastroIntestinalSystem_sum_lsoa,
EarNoseandOropharynx_sum_lsoa,
Eye_sum_lsoa,
EndocrineSystem_sum_lsoa,
CentralNervousSystem_sum_lsoa,
Cardio_sum_lsoa
)

str(my.df.list)
str(MalignantDiseaseImmunosuppression_sum_lsoa)



Alldrugsdf <-do.call("rbind", my.df.list)

str(Alldrugsdf)
unique(Alldrugsdf$Drug)
feather::write_feather(Alldrugsdf,"alldrugsdf.feather")



```
```{r}
getwd()
# rm(list=ls())

Alldrugsdf<-feather::read_feather("alldrugsdf.feather")

##colnames(Alldrugsdf)
##unique(Alldrugsdf$Drug)
##unique(Alldrugsdf$month)

ukpostcode<-read_csv("ukpostcode_data.csv")

colnames(ukpostcode)

postcode_lookup<-read_csv("postcode_lookup.csv")

lsoa_lookup <- postcode_lookup %>% dplyr::select(lsoa,nuts3,nuts1) %>% as.data.frame() %>% unique()

## nrow(lsoa_lookup)
## nrow(unique(lsoa_lookup))

## str(lsoa_lookup)

## rm(Alldrugsdf) rm(postcode_lookup) rm(ukpostcode)

alldrugsdf_nuts<-dplyr::inner_join(Alldrugsdf,lsoa_lookup,by="lsoa")

feather::write_feather(alldrugsdf_nuts,"alldrugsdf_nuts.feather")

# alldrugsdf_nuts<-feather::read_feather("alldrugsdf_nuts.feather")

clustereddset<-feather::read_feather("C:\\Users\\Peter\\Downloads\\DoordaOutput\\overalldsetclusterlabelled.feather")

load(file="C:\\Users\\Peter\\Downloads\\DoordaOutput\\hierarchical_clustering_ward_D2_16_02_2018_expanded_inputset.rda")

grp<-cutree(rs.hc.pca10,k=7)


grp.df<- grp %>% as.data.frame()

overall_dset_k7<-cbind(clustereddset,grp.df)

clustereddset_alldrugsdf<-dplyr::inner_join(alldrugsdf_nuts,overall_dset_k7,by="lsoa")

colnames(clustereddset_alldrugsdf)[135]<-"cluster"

feather::write_feather(clustereddset_alldrugsdf,"clustereddset_alldrugsdf.feather")



```

